An elaborate data set on human gait and the effect of mechanical perturbations

### 2015-03-10 paper.tex
Footnote about baseball cap. Fixes 122.

\subsection*{Protocol}
%
The experimental protocol consisted of both static measurements and walking on
the treadmill for 10 minutes under unperturbed and perturbed conditions. Before
a set of trials on the same day, the motion capture system was calibrated using
the manufacturer's recommended procedure. Before each subject's gait data were
collected, the subject changed into athletic shoes, shorts, a sports bra,
a baseball cap, and a rock climbing harness. All 47 markers were applied
directly to the skin at the landmarks noted in Table~\ref{tab:marker-labels}
except for the heel, toe, and head markers, which were placed on the respective
article of clothing.~\footnote{The sacrum and rear pelvic markers may have been
placed on the shorts for a small number of the subjects.} Then the subject
self-reported their age, gender, and mass. Finally, their height was measured
by the experimentalist and four reference photographs (front, back, right,
left) were taken of subject's marker locations.

>>>>

\subsection*{Protocol}
%
The experimental protocol consisted of both static measurements and walking on
the treadmill for 10 minutes under unperturbed and perturbed conditions. Before
a set of trials on the same day, the motion capture system was calibrated using
the manufacturer's recommended procedure. Before each subject's gait data were
collected, the subject changed into athletic shoes, shorts, a sports bra,
a baseball cap~\footnote{A cap was used to avoid having to shave participants'
hair but at the expense of accuracy.}, and a rock climbing harness. All 47 markers
were applied directly to the skin at the landmarks noted in
Table~\ref{tab:marker-labels} except for the heel, toe, and head markers, which
were placed on the respective article of clothing.~\footnote{The sacrum and
rear pelvic markers may have been placed on the shorts for a small number of
the subjects.} Then the subject self-reported their age, gender, and mass.
Finally, their height was measured by the experimentalist and four reference
photographs (front, back, right, left) were taken of subject's marker
locations.
